\thetitle

### 2020-07-01 writing/paper.tex
fix basic latex mistakes in rudimentary way
no ACM footer to make space for real content
abstract

%% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
\documentclass[acmsmall,screen]{acmart}\settopmatter{printfolios=true,printccs=true,printacmref=true}
%% For double-blind review submission, w/ CCS and ACM Reference
%%\documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true}
%% For single-blind review submission, w/o CCS and ACM Reference (max submission space)
%\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For single-blind review submission, w/ CCS and ACM Reference
%\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission, w/ required CCS and ACM Reference
%\documentclass[acmsmall]{acmart}\settopmatter{}

@@

%\author[]{}
%\affiliation{
%\institution{}
%% \city{}
%% \city{}
% \country{}
%}
%\email{}          %% \email is recommended

@@

%%%
\setcopyright{}
\acmPrice{}
\acmDOI{}
\acmYear{}
\copyrightyear{}
\acmJournal{}
\acmVolume{}
\acmNumber{}
\acmArticle{}
\acmMonth{}

@@

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
Gradual types and blame go hand in hand. But what is the value of blame?
\end{abstract}

@@

\input{introduction.tex} \label{sec:introduction}
\input{landscape.tex} \label{sec:landscape}
\input{ideas.tex} \label{sec:ideas}
\input{experiment.tex} \label{sec:experiment}
\input{results.tex} \label{sec:results}
\input{discussion.tex} \label{sec:discussion}
\input{related.tex} \label{sec:related}
\input{conclusion.tex} \label{sec:conclusion}

>>>>

%% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
\documentclass[acmsmall,screen,anonymous,nonacm]{acmart}\settopmatter{printfolios=true,printccs=true,printacmref=true}
%% For double-blind review submission, w/ CCS and ACM Reference
%%\documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true}
%% For single-blind review submission, w/o CCS and ACM Reference (max submission space)
%\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For single-blind review submission, w/ CCS and ACM Reference
%\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission, w/ required CCS and ACM Reference
%\documentclass[acmsmall]{acmart}\settopmatter{}

@@

\author{Nobody In Particular}
% \affiliation{\institution{PLT} \city{Evanston} \country{Illinois} }
\affiliation{\relax} % \institution{PLT} \city{Evanston} \country{Illinois} }
% \email{chrdim@northwestern.edu}          %% \email is recommended

@@

%%%
\setcopyright{none}
\acmPrice{1}
\acmDOI{}
\acmYear{}
\copyrightyear{}
\acmJournal{pacmpl}
\acmVolume{1}
\acmNumber{1}
\acmArticle{1}
\acmMonth{1}

@@

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
Programming language theoreticians develop blame assignment systems
and prove blame theorems for gradually typed programming languages.
Practical implementations of gradual typing almost completely ignore
the idea of blame assignment.  This contrast raises the question
whether blame assignment provides any value to the working programmer
and poses the challenge of how to evaluate the effectiveness of blame
assignment systems. This paper contributes (1) the first evaluation
method for blame assignment systems and (2) the results from applying
it to three different systems. \mf{This sentence must be checked
before final submission.} These results confirm that blame assignment
is helpful to a rationally acting programmer.
\end{abstract}

@@

\input{introduction.tex} \label{sec:introduction}
\input{landscape.tex}    \label{sec:landscape}
\input{challenges.tex}   \label{sec:challengs}
\input{ideas.tex}        \label{sec:ideas}
\input{experiment.tex}   \label{sec:experiment}
\input{results.tex}      \label{sec:results}
\input{discussion.tex}   \label{sec:discussion}
\input{related.tex}      \label{sec:related}
\input{conclusion.tex}   \label{sec:conclusion}
